---
title: "fp_ms_6.Rmd"
author: "Hamaad Mehal"
date: "4/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(gt)
library(ggplot2)
library(janitor)
library(devtools)
library(rvest)
library(haven)
library(magrittr)
library(infer)
```
The biggest limitation to this graph was my x-axis, which I will learn to clean up at my TF meeting. The code was seemingly sound for it, but it would not work. This just one of many sets of visual graphs I will employ in my project, and I wanted to include this set to get input on my approach before I delve into creating more visuals for my final project. My GitHub is at: https://github.com/hamaadwmehal/ms_4 . Go into ms_5 to see my code and look at my attempts at cleaning up the x-axis.

```{r, include = FALSE}
url <- paste0("https://www.spotrac.com/nba/fines-suspensions/") 
h <- read_html(url)
class(h)
h
html_text(h)
tab <- h %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:661)
tab
```

```{r, include = FALSE}
count_fine <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(1:661) 

count_fine
```

```{r, echo = FALSE}
ggplot(count_fine, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Players") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020") +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank())

ggsave("fp_ms_6_shiny/count_fine_1.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine1 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(1:25) 

count_fine1
```

```{r, echo = FALSE}
ggplot(count_fine1, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Top 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
ggsave("fp_ms_6_shiny/count_fine_2.png", width = 10, height = 10)

```

```{r, include = FALSE}
count_fine2 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(26:50) 

count_fine2
```

```{r, echo = FALSE}
ggplot(count_fine2, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Second 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggsave("fp_ms_6_shiny/count_fine_3.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine3 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(51:75) 

count_fine3
```

```{r, echo = FALSE}
ggplot(count_fine3, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Third 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
ggsave("fp_ms_6_shiny/count_fine_4.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine4 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(76:100) 

count_fine4
```

```{r, echo = FALSE}
ggplot(count_fine4, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Fourth 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
ggsave("fp_ms_6_shiny/count_fine_5.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine5 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(101:125) 

count_fine5
```

```{r, echo = FALSE}
ggplot(count_fine5, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Fifth 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggsave("fp_ms_6_shiny/count_fine_6.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine6 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(126:150) 

count_fine6
```

```{r, echo = FALSE}
ggplot(count_fine6, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Sixth 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
ggsave("fp_ms_6_shiny/count_fine_7.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine7 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(150:175) 

count_fine7
```

```{r, echo = FALSE}
ggplot(count_fine7, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Seventh 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggsave("fp_ms_6_shiny/count_fine_8.png", width = 10, height = 10)
```

```{r, include = FALSE}
count_fine8 <- tab %>%
  select(Player) %>%
  mutate(Player = as_factor(Player)) %>% 
  count(Player) %>%
  arrange(desc(n)) %>%
  mutate(rank = rank(-n)) %>%
  slice(150:175) 

count_fine8
```

```{r, echo = FALSE}
ggplot(count_fine8, aes(x = Player, y = n, color = n)) +
  geom_col() +
  xlab(label = "Player") +
  ylab(label = "Number of Fines") +
  labs(title = "Number of Fines Per NBA Player in 2019-2020, Eighth 25") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
ggsave("fp_ms_6_shiny/count_fine_9.png", width = 10, height = 10)
```