---
title: "Milestone #4"
author: "Hamaad Mehal"
date: "3/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(gt)
library(ggplot2)
library(janitor)
library(devtools)
library(rvest)
```

My repository url is: https://github.com/hamaadwmehal/ms_4.git 

```{r}
url <- paste0("https://www.spotrac.com/nba/fines-suspensions/") 
h <- read_html(url)
class(h)
h
html_text(h)
tab <- h %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:661)
tab
```


```{r, include = FALSE}
url1 <- paste0("https://www.spotrac.com/nba/fines-suspensions/2018/") 
h1 <- read_html(url1)
class(h1)
h1
html_text(h1)
tab1 <- h1 %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:1028)
tab1
```


```{r, include = FALSE}
url2 <- paste0("http://www.espn.com/nba/salaries") 
h2 <- read_html(url2)
class(h2)
h2
html_text(h2)
tab2 <- h2 %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:521)
tab2
```


```{r, include = FALSE}
url3 <- paste0("http://www.espn.com/nba/salaries/_/year/2019") 
h3 <- read_html(url3)
class(h3)
h3
html_text(h3)
tab3 <- h3 %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:503)
tab3
```


```{r, include = FALSE}
url4 <- paste0("https://www.basketball-reference.com/leagues/NBA_2020_standings.html") 
h4 <- read_html(url4)
class(h4)
h4
html_text(h4)
tab4 <- h4 %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:15)
tab4
```

```{r, include = FALSE}
url5 <- paste0("https://www.basketball-reference.com/leagues/NBA_2020_standings.html") 
h5 <- read_html(url5)
class(h5)
h5
html_text(h5)
tab5 <- h5 %>% html_nodes("table") %>%
.[[2]] %>%
html_table() %>%
slice(1:15)
tab5
```
```{r, include = FALSE}
url6 <- paste0("https://www.basketball-reference.com/leagues/NBA_2019_standings.html") 
h6 <- read_html(url6)
class(h6)
h6
html_text(h6)
tab6 <- h6 %>% html_nodes("table") %>%
.[[1]] %>%
html_table() %>%
slice(1:15)
tab6
```

```{r, include = FALSE}
url7 <- paste0("https://www.basketball-reference.com/leagues/NBA_2019_standings.html") 
h7 <- read_html(url7)
class(h7)
h7
html_text(h7)
tab7 <- h7 %>% html_nodes("table") %>%
.[[2]] %>%
html_table() %>%
slice(1:15)
tab7
```
I got my data on NBA salaries from ESPN and my data on NBA fines for players
and teams from spotrac.com. I also got NBA team standings data from basketball
-reference.com which has all data relating to wins and losses. I want to join 
the data by players' and teams' names to get the fine data and salary data per 
player in one table. I want to see the percentage of the player's salary taken 
by the average of all the fines they amassed and see whether the incidences of 
them getting fined again changes by the proportion of the fine (number of times 
fined). I also want to evaluate teams' performance by fine data and see whether 
success is related to team performance. My plan is to get this data from 1999 
until now as that is how far the data seems to stretch, and I believe my next 
plan of action will be to collect the rest fo the years' fine and salary data 
before joining tables by year/name and evaluating the table. Lastly, I would 
put the information in 20 graphs to see whether the data visually is similar 
every year and whether percentage of salary makes a difference in recurring 
fines for players. 